Stool Microbiome Analysis

### 2022-01-05 Rmarkdown/analysis/Fecal_Microbiome_TMAO_Analysis_211105.Rmd
Investigate tnf-a (WIP)

>>>>

Save for supplemental material
```{r Save linear regression results with bacteria}
write.csv(res_des, "../../Outputs/tables/Microbiome/LinReg_cardiometabolic_withDESeq2results.csv")
saveRDS(res_des, "../../Outputs/tables/Microbiome/LinReg_cardiometabolic_withDESeq2results.Rds")
```

Is TNF-a related to the gut microbiome directly?
## Factored by tnfa Tertile

THIS CHUNK WORK IN PROGRESS

```{r DESeq2 analysis - tnf-a tertile}
# Quick check
summary(lm(tnfa_bd1_ln ~ f__Bacteroidaceae_g__Bacteroides, phen_sub)) # NS
summary(lm(tnfa_bd1_ln ~ f__Peptostreptococcaceae_g__, phen_sub)) # Sig, minor inverse relationship
summary(lm(tnfa_bd1_ln ~ f__Christensenellaceae_g__, phen_sub)) # NS
summary(lm(tnfa_bd1_ln ~ f__Lachnospiraceae_g__Butyrivibrio, phen_sub)) # NS
# With covariates
summary(lm(tnfa_bd1_ln ~ f__Bacteroidaceae_g__Bacteroides + sex + age + bmi_final, phen_sub)) # NS
summary(lm(tnfa_bd1_ln ~ f__Peptostreptococcaceae_g__ + sex + age + bmi_final, phen_sub)) # Sig, minor inverse relationship
summary(lm(tnfa_bd1_ln ~ f__Christensenellaceae_g__ + sex + age + bmi_final, phen_sub)) # NS
summary(lm(tnfa_bd1_ln ~ f__Lachnospiraceae_g__Butyrivibrio + sex + age + bmi_final, phen_sub)) # NS

# Now see about differential abundance with TNF-a (THIS PART WORK IN PROGRESS)
# Add TNF-a to PSOtmao1G
phen_tnfa <- subset(phen, select=c(tnfa_bd1))
sample_data(PSOtmao1G)$tnfa_bd1 <- merge(sample_data(PSOtmao1G), phen_tnfa, by = 0)

# Add TNF-a tertile
tnfa_tertile <- quantile(sample_data(PSOtmao1G)$tnfa_bd1, c(0:3/3), na.rm = TRUE)
sample_data(PSOtmao)$tmao_tertile <- ifelse(sample_data(PSOtmao)$tmao <= tmao_tertile[2], "Tertile1",
                             ifelse(sample_data(PSOtmao)$tmao > tmao_tertile[2] & sample_data(PSOtmao)$tmao <= tmao_tertile[3], "Tertile2", "Tertile3"))
# Factor it
sample_data(PSOtmao)$tmao_tertile = factor(sample_data(PSOtmao)$tmao_tertile)
# Lookss good
table(sample_data(PSOtmao)$tmao_tertile)

# DESeq analysis - tmao_tertile
mb <- phyloseq_to_deseq2(PSOtmao1G, ~ sex + age + bmi_final.x + tmao_tertile)
mb.ratio <- DESeq(mb, test = "LRT", reduced = ~ sex + age + bmi_final.x) # remove variable of interest here, TMAO
res.ratio <- results(mb.ratio, contrast = c("tmao_tertile", "Tertile1", "Tertile3")) # Look at most different tertiles
alpha = 0.05
sigtab = res.ratio[which(res.ratio$padj < alpha), ]
sigtab = cbind(as(sigtab, "data.frame"), as(tax_table(PSOtmao1G)[rownames(sigtab), ], "matrix"))
sigtab$family_genus <- paste0(sigtab$Family, sigtab$Genus)
head(sigtab)

# Save
tiff("../../Outputs/plots/microbiome/DESeq2_Genus_tnfa_TMAOTertile1v3_2112.tiff", width = 8, height = 3, units = 'in', res = 300)
DESeqPlot
dev.off()
```
